Stochastic Variance Reduced Policy Gradient

### 2018-02-02 svrpg.tex
correzioni

\section{Hyperparameters}\label{sec:stopping}
In Reinforcement learning we have to take into account the gradient's variance.
\todomat{$\uparrow$ the opening of the section could connect better with previous sections. Declare which meta-parameters will be addressed in the section}
A common way to reduce the effect of variance is to use Adaptive Moment Estimation (Adam) \cite{kingma2014adam}, a method that computes adaptive learning rates for each parameter. Adam helps to stabilize the gradient estimate by computing adaptive learning rates for each parameter based on the history of the gradients' variance.
Due to this feature we can use two different adam in order to properly leverage the structure of the proposed SVRPG update. The first adam will be associated to the snapshot updates and the second one will be associated to the sub-iteration updates. By doing so we are decoupling the contribution to the variance introduced by the snapshots from that one introduced by the sub-iterations, which lie, respectively, on two different order of magnitude.Therefore, we are able to properly adapt the learning rate in each situation. 
\todomat{$\uparrow$ explain better: it's not only two separate meta-parameters, but two separate learning rate schedules. Use notation from previous sections, \eg snaphot is usually associated with $\tilde{\vtheta}$} 
This is because we are dealing with two different variance magnitudes.
\todomat{$\uparrow$ the reason is this, but try to spend more words on it}
Denote by $\alpha_{snap}$ the learning rate associated to the last snapshot and denote by  $\alpha_{sub-iter}$ the learning rate associated to the current sub-iteration.

@@

In order to cope with this behaviour we introduce an adaptive stopping condition: we permorm a new snapshot anytime the weighted learning rate proposed by the adam optimizer in a sub-iteration is smaller than the weighted one proposed at the immediately previous snapshot. This stopping condition is subject to a constraint on the maximum number of sub-iterations performable, which is problem dependent.
\todomat{I find "two stopping conditions" confusing: it's just one with an additional constraint}
\todobep{I tried to solve the issue here:hope it's better now}
More precisely we stop performing sub-iterations when:

@@

\todomat{why? should mention how this formula combines trajectory efficiency and variance control}
\todobep{also here I tried to solve the issues highlighted}

>>>>

\section{Hyperparameters}\label{sec:stopping}
In Reinforcement learning we have to take into account the gradient's variance.
\todomat{$\uparrow$ the opening of the section could connect better with previous sections. Declare which meta-parameters will be addressed in the section}
A common way to reduce the effect of variance is to use Adaptive Moment Estimation (Adam) \cite{kingma2014adam}, a method that computes adaptive learning rates for each parameter. Adam helps to stabilize the gradient estimate by computing adaptive learning rates for each parameter based on the history of the gradients' variance.
Due to this feature we can use two different adam in order to properly leverage the structure of the proposed SVRPG update. The first adam will be associated to the snapshot updates and the second one will be associated to the sub-iteration updates. By doing so we are decoupling the contribution to the variance introduced by the snapshots from that one introduced by the sub-iterations. These two variance contributions lie, respectively, on two different order of magnitude because the number of trajectories used to perform the estimates for the snapshot is greater than that used for a sub-iteration.Therefore, using two adam optimizers allows us to properly adapt the learning rate in each situation. 
Denote by $\alpha_{snap}$ the learning rate associated to the last snapshot and denote by  $\alpha_{sub-iter}$ the learning rate associated to the current sub-iteration.

@@

In order to cope with this behaviour we introduce an adaptive stopping condition: we permorm a new snapshot anytime the weighted learning rate proposed by the adam optimizer in a sub-iteration is smaller than the weighted one proposed at the immediately previous snapshot. This stopping condition is subject to a constraint on the maximum number of sub-iterations performable, which is problem dependent.
More precisely we stop performing sub-iterations when:

@@
